Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-01 ms.qmd
Did not fix the in line eqn

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}_{acute}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).

>>>>

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
